---
title: "EGM_Group_Assignment"
author: "Mehtap Colak, Tugce Uncu, Bulent Buyuk, Oguz Colak"
date: "07 11 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1.Introduction

This is a worksheet of EGM Group Assignment.

The project's dataset includes key indicators of Individual Pension System from the August 2014 through July 2019.


# 2.Import EGM Dataset

First, We downloaded dataset from the [EGM website](https://www.egm.org.tr/bilgi-merkezi/istatistikler/), then the "Rapor Tarihi" filter removed and put in the dataset as new column. 

Finally in this step, we import the dataset to R Studio.

````{r}

library(readxl)
egm_data<- read_excel("EGM_Dataset.xlsx",skip=2,col_names=FALSE)

````


# 3. Loading Libraries & Data Transformation

We import packages we'll use at this step.

We've changed column names and date format.

Then we checked the dataset wtih head&tail functions.

```{r warning=FALSE,message=FALSE}

library(tidyverse)
library(formattable)
library(ggplot2)
library(lubridate)

names(egm_data) <- c("tarih", "sirket_adi", "katilimci_sayisi", "katilimci_fon_tutari", "devlet_katkisi_tutari", "katki_payi_tutari", "emekli_katilimci_sayisi", "bireysel_sozlesme_sss", "grup_bireysel_sozlesme_sss", "isveren_grup_sertifika_sss", "toplam_sss", "bireysel_sozlesme_yyt", "grup_bireysel_sozlesme_yyt", "isveren_grup_sertifika_yyt", "toplam_yyt")

egm_data$tarih <- ymd(egm_data$tarih)

head(egm_data)
tail(egm_data)
```


# 4. Analysis

## Mean Participant in First 20 Companies

```{r warning=FALSE,message=FALSE}

mean_participant_list <- egm_data %>%
  group_by(sirket_adi) %>% arrange(sirket_adi) %>%
  summarise(mean_participant = mean(katilimci_sayisi/1000000)) %>%
  arrange(desc(mean_participant)) %>%
  top_n(20)


ggplot(mean_participant_list,aes(x=sirket_adi, y = mean_participant))+
  geom_bar(stat ="identity")+
  theme(axis.text.x = element_text(angle=90))
```

## Best 10 Companies in Market Share

```{r Best 10 Companies}

head_10_by_pazar_payi <- egm_data %>% 
  group_by(sirket_adi) %>%
  summarise(ortalama_fon_tutari=mean(katilimci_fon_tutari, na.rm = TRUE)) %>%
  mutate(pazar_payi = percent(ortalama_fon_tutari / sum(ortalama_fon_tutari))) %>%
  top_n(10, pazar_payi)

print(head_10_by_pazar_payi)


# Plot: Top 10 Companies by Market Share (Mean Participant Funds):

ggplot(data = head_10_by_pazar_payi, aes(x=sirket_adi, y=pazar_payi, fill=sirket_adi)) +
  geom_bar(stat="identity")+
  coord_polar()+
  theme(legend.position = "right", axis.text.x = element_text(angle = 0))+
  geom_text(aes(y = pazar_payi , label = pazar_payi))+
  labs(title = "Best 10 Company in Market Share", x="", y="")

```

## Total Yearly Company Size

```{r analyize 2}

aa <- egm_data %>% mutate(YEAR = year(tarih)) %>%  
  group_by(sirket_adi, YEAR) %>%
  summarise(sum_size_total=sum(toplam_yyt)) %>%
  arrange(desc(sum_size_total)) %>%
  filter(sum_size_total > 165000000000) 
  print(aa)
  
  
  aa %>%
  ggplot(data = ., aes(x = sirket_adi, y = sum_size_total, fill = sirket_adi)) +
      geom_bar(stat = "identity") + theme(axis.text = element_text(angle = 90)) +
  facet_wrap(~ YEAR, ncol = 3) + labs(title = "Total Yearly Company Size",
           subtitle = "Data plotted by year",
           y = "Sum size total",
           x = "Company") 
```