---
title: "Group Project P3 Data"
output: html_document
---

```{r warning=FALSE,message=FALSE}
library(tidyverse)
library(rvest)
library(ggplot2)
library(scales)
library(dplyr)
```

## Acquisition and Introduction of the Data

```{r setup, warning=FALSE,message=FALSE}
# Temporary file for "Planning"
planning_temp=tempfile(fileext=".xlsx")
# Temporary file for "Production"
production_temp=tempfile(fileext=".xlsx")
# Temporary file for "Consumption"
consumption_temp=tempfile(fileext=".xlsx")

# Downloading file from repository to the "Planning" temp
download.file("https://raw.githubusercontent.com/pjournal/mef03g-Kar-R-sizlar/master/4-year-planning.csv?raw=true",destfile=planning_temp,mode='wb')
# Downloading file from repository to the "Production" temp
download.file("https://raw.githubusercontent.com/pjournal/mef03g-Kar-R-sizlar/master/4-year-production.csv?raw=true",destfile=production_temp,mode='wb')
# Downloading file from repository to the "Consumption" temp
download.file("https://raw.githubusercontent.com/pjournal/mef03g-Kar-R-sizlar/master/4-year-consumption.csv?raw=true",destfile=consumption_temp,mode='wb')

# Reading the csv files.
planning_raw_data=read.csv(planning_temp,skip=1)
production_raw_data=read.csv(production_temp,skip=1)
consumption_raw_data=read.csv(consumption_temp,skip=1)

# Removing the temp files
file.remove(planning_temp)
file.remove(production_temp)
file.remove(consumption_temp)
```

### Preparation and Introduction of Planning Data

* 4 Year Planning Data: This data includes 33599 rows and 15 variables for the planned pruduction between January 1st, 2016 and October 31st, 2019

```{r}
# Proper Column Names
colnames(planning_raw_data) <-  c('tarih', 'saat', 'toplam_mwh', 'dogal_gaz', 'ruzgar', 'linyit', 'tas_komur', 'ithal_komur', 'fuel_oil', 'jeotermal', 'barajli', 'nafta', 'biyokutle', 'akarsu', 'diger')
# Proper Data Format
planning_raw_data[,3:15]  <- as.data.frame(lapply(planning_raw_data[,3:15], function(x) as.numeric(gsub(",", ".", gsub("\\.", "", x)))))
planning_raw_data$tarih <-as.character(planning_raw_data$tarih)
planning_raw_data$saat <-as.character(planning_raw_data$saat)
head(planning_raw_data, 10)
```

### Preparation and Introduction of Production Data

* 4 Year Production Data: This data includes 33597 rows and 18 variables for the actual pruduction between January 1st, 2016 and October 31st, 2019

```{r}
# Defining Column Names
colnames(production_raw_data) <-  c('tarih', 'saat', 'toplam_mwh', 'dogal_gaz', 'barajli', 'linyit', 'akarsu', 'ithal_komur', 'ruzgar', 'gunes', 'fuel_oil', 'jeotermal', 'asfaltit_komur', 'tas_komur', 'biyokutle', 'nafta', 'lng', 'uluslararasi')
# Proper Data Format
production_raw_data[,3:18]  <- as.data.frame(lapply(production_raw_data[,3:18], function(x) as.numeric(gsub(",", ".", gsub("\\.", "", x)))))
production_raw_data$tarih <-as.character(production_raw_data$tarih)
production_raw_data$saat <-as.character(production_raw_data$saat)
head(production_raw_data, 10)
```

### Preparation and Introduction of Consumption Data

* 4 Year Consumpiton Data: This data includes 33575 rows and 3 variables for actual consumption between January 1st, 2016 and October 31st, 2019

```{r}
# Defining Column Names
colnames(consumption_raw_data) <-  c('tarih', 'saat', 'tuketim_miktari_mwh')
# Proper Data Format
consumption_raw_data <-  cbind(consumption_raw_data, consumption_raw_data)
consumption_raw_data[,3:6]  <- as.data.frame(lapply(consumption_raw_data[,3:6], function(x) as.numeric(gsub(",", ".", gsub("\\.", "", x)))))
consumption_raw_data <- consumption_raw_data[, 1:3]
consumption_raw_data$tarih <-as.character(consumption_raw_data$tarih)
consumption_raw_data$saat <-as.character(consumption_raw_data$saat)
head(consumption_raw_data, 10)
```
